$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-06 paper/e6ssm-tuning-paper.tex
Removed terms from two-loop beta for y_t that appear to be due to a SARAH bug (in the coefficient of g_1^2g_1'^2)
Added two-loop beta for a_t, neglecting the additional terms that appear in the SARAH output. As written the beta function matches the one given in the CE6SSM paper, which should be correct
Removed additional U(1)_Y x U(1)' trace appearing in coefficient of g_1^2g_1'^2 in two-loop beta function for lambda. As for y_t, having this trace means 1) the coefficient doesn't match up with that given in the CE6SSM paper and 2) extra terms appear in the two-loop beta function for A_t, which

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we find that, for the points satisfying the current limit on the mass of the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the minimum fine tuning that can be achieved is 
$\Delta_{\textrm{min}}\approx 121$.

If run II of the LHC further pushes up the limit on the $Z^\prime$
mass to be above $4.5$ TeV then the fine tuning in the model will be
greater than at least $\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$ GeV and $125.5$ GeV.

@@

In the top panel one can see that the MSSM BM1 tuning 
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the middle left confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top panel. In this case we have chosen a
point with large mixing, which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall for the points we looked at.

@@

In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
model. With the exception of the parameters $m_{Q3}^2$, 
$m_{u3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
$M_{1/2}=1003$ GeV, $A_0=500$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ and
$\lambda_{1,2}(M_X)=0.1$. This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$. Here we define
\begin{align*}
\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Qi}^2+3m_{ui}^2+6m_{di}^2+m_{ei}^2+4m_{Li}^2-4m_{H_{ui}}^2-6m_{H_{di}}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{Di}^2\right )\\
&\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
\end{align*}
In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$. In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms. Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2-Q_1\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\

@@

&{}+\lambda \left [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\right.\nonumber\\
&{}\left.+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
\beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\

@@

&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\

@@

\beta_{a_t}^{(2)}&=,\label{eq:USSMTYu22BetaTwoLoop}\\

@@

b_{m_{Q3}^2}^{(2)}&=.\label{eq:USSMmq222Ot2Coeff}

@@

&{}+12Q_ug_1^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
&{}+12Q_ua_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ua_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
&{}+Q_ug_1'^2\sum_{i=1}^3\bigg [ 6\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
&{}+4\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\

@@

&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )( 9Q_d^2+9Q_D^2+9Q_{\overline{D}}^2+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2\nonumber\\
&{}+6Q_L^2+18Q_Q^2+3Q_S^2+9Q_u^2 )\big ].\label{eq:USSMmu222Ot2Coeff}

>>>>

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we
find that, for the points satisfying the current limit on the mass of
the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
minimum fine tuning that can be achieved is
$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least
$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
GeV and $125.5$ GeV.

@@

In the top panel one can see that the MSSM BM1 tuning (green curve) 
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the middle left confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top panel. In this case we have chosen a
point with large mixing, which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall for the points we looked at.

@@

In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
model. With the exception of the parameters $m_{Q3}^2$, 
$m_{u3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
$M_{1/2}=1003$ GeV, $A_0=500$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ and
$\lambda_{1,2}(M_X)=0.1$. This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$. Here we define for the E$_6$SSM (see also Eqs.~(\ref{eq:USSMGaugeSigmaTerm1}-\ref{eq:USSMGaugeSigmaTerm1Pr}) for general $U(1)$ inspired models)
\begin{align*}
\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Qi}^2+3m_{ui}^2+6m_{di}^2+m_{ei}^2+4m_{Li}^2-4m_{H_{ui}}^2-6m_{H_{di}}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{Di}^2\right )\\
&\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
\end{align*}
In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$. In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms. Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\

@@

&{}+\lambda \bigg [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\nonumber\\
&{}+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\bigg ],\label{eq:USSMTLambdaBetaOneLoop}\\
\beta_{a_\lambda}^{(2)}&=a_\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \}+\lambda \bigg \{ -4\lambda a_\lambda \left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )\nonumber\\
&{}-4\lambda^2\left ( \lambda a_\lambda+2\Sigma_{a_\lambda}+3\Sigma_{a_\kappa}\right )-16\Pi_{a_\lambda}-24\Pi_{a_\kappa}-6\lambda a_\lambda\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
&{}-6\lambda^2\left ( 3y_ta_t+3y_ba_b+y_\tau a_\tau\right )-12\left [ 3y_t^3a_t+3y_b^3a_b+y_ty_b\left ( y_ta_b+y_ba_t\right )+y_\tau^3 a_\tau\right ]\nonumber\\
&{}+32g_3^2\left [ y_ta_t+y_ba_b+\Sigma_{a_\kappa}-\left ( y_t^2+y_b^2+\Sigma_\kappa\right )M_3\right ]+12g_2^2\left ( \Sigma_{a_\lambda}-\Sigma_\lambda M_2\right )\nonumber\\
&{}+\frac{2}{5}g_1^2\left [ 4y_ta_t-2y_ba_b+6y_\tau a_\tau+4\Sigma_{a_\kappa}+6\Sigma_{a_\lambda}-2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa+3\Sigma_\lambda\right )M_1\right ]\nonumber\\
&{}+4g_1'^2\big [ 3y_t\left ( Q_Q^2-Q_2^2+Q_u^2\right )\left ( a_t-y_t M_1'\right )+3y_b\left ( Q_Q^2-Q_1^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\nonumber\\
&{}+y_\tau\left ( Q_L^2-Q_1^2+Q_e^2\right )\left ( a_\tau-y_\tau M_1'\right )+2Q_S^2\lambda\left ( a_\lambda-\lambda M_1'\right )\nonumber\\
&{}+2\left ( Q_1^2+Q_2^2-Q_S^2\right )\left ( \Sigma_{a_\lambda}-\Sigma_\lambda M_1'\right )+3\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\left ( \Sigma_{a_\kappa}-\Sigma_\kappa M_1'\right ) \big ]\nonumber\\
&{}-66g_2^4M_2-\frac{594}{25}g_1^4M_1-8g_1'^4M_1'\left [ 2\left ( Q_1^4+Q_2^4+Q_S^4\right )+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_Q\right ]\nonumber\\
&{}-\frac{18}{5}g_2^2g_1^2\left ( M_2+M_1\right )-12g_2^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_2+M_1'\right )\nonumber\\
&{}-\frac{12}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTLambdaBetaTwoLoop}\\

@@

&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\

@@

\beta_{a_t}^{(2)}&=a_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \}+y_t\bigg \{ -88y_t^3a_t-20y_b^3a_b-10y_ty_b\left ( y_ba_t+y_ta_b\right )\nonumber\\
&{}-2y_by_\tau\left ( y_b a_\tau+y_\tau a_b\right )-2\lambda a_\lambda \left ( 2\lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa\right )\nonumber\\
&{}-2\lambda^2\left ( 3y_t a_t+4y_b a_b+y_\tau a_\tau +2\Sigma_{a_\lambda}+3\Sigma_{a_\kappa}\right )+32g_3^2y_t\left ( a_t-y_tM_3\right )\nonumber\\
&{}+12g_2^2y_t\left ( a_t-y_tM_2\right )+\frac{2}{5}g_1^2\left [ 6y_ta_t+2y_ba_b-\left ( 6y_t^2+2y_b^2\right )M_1\right ]\nonumber\\
&{}+4g_1'^2\big [ \lambda\left (Q_1^2-Q_2^2+Q_S^2\right ) \left ( a_\lambda-\lambda M_1'\right )+2y_t\left ( 2Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )\nonumber\\
&{}+y_b\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\big ]-\frac{512}{9}g_3^4M_3-66g_2^4M_2-\frac{7826}{225}g_1^4M_1\nonumber\\
&{}-8g_1'^4M_1'\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]-16g_3^2g_2^2\left ( M_3+M_2\right )\nonumber\\
&{}-\frac{272}{45}g_3^2g_1^2\left ( M_3+M_1\right )-\frac{64}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )\left ( M_3+M_1'\right )-2g_2^2g_1^2\left ( M_2+M_1\right )\nonumber\\
&{}-12g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\left ( M_2+M_1'\right )-\frac{4}{15}g_1^2g_1'^2\left ( 9Q_2^2+Q_Q^2+16Q_u^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTYu22BetaTwoLoop}\\

@@

b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u^2}+m_{Q3}^2+m_{u3}^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+48y_t^2a_t^2+48y_b^2a_b^2\nonumber\\
&{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )+4\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
&{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2\right )+2\left ( y_\tau a_b+y_ba_\tau\right )^2\nonumber\\
&{}+2\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+2\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
&{}+2\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+2\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
&{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
&{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
&{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-6g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
&{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_2^2\right )-6g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
&{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{26}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
&{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1^2\right )-\frac{14}{15}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
&{}-4g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )-4g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+2g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 6Q_Qm_{H_u}^2+6Q_Qm_{Q3}^2+6Q_Qm_{u3}^2+\Sigma_1'\right )\nonumber\\
&{}+12Q_Qg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )-4g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )\nonumber\\
&{}-4g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )+2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\times\nonumber\\
&{}\times\left ( 6Q_Qm_{H_d}^2+6Q_Qm_{Q3}^2+6Q_Qm_{d3}^2+\Sigma_1'\right )+12Q_Qg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
&{}+4Q_Qg_1'^2y_\tau^2\left (Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_Qg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
&{}+2Q_Qg_1'^2\sum_{i=1}^3\Big [ 2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\nonumber\\
&{}+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
&{}-96Q_Qg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
&{}-12Q_Qg_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )+\frac{96}{25}g_1^4\left ( \Sigma_1-M_1^2\right )\nonumber\\
&{}-\frac{1}{5}g_1^2g_1'^2\big [ 12Q_QM_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}+3Q_L\nonumber\\
&{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
&{}-Q_{H'}-3Q_L+3Q_Q-6Q_u\big )\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
&{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_QM_1'^2-\Sigma_1'\right )\Sigma_Q\big ].\label{eq:USSMmq222Ot2Coeff}

@@

&{}+12Q_ug_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
&{}+12Q_ug_1'^2a_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ug_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
&{}+2Q_ug_1'^2\sum_{i=1}^3\bigg [ 3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
&{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\

@@

&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )\Sigma_Q\big ].\label{eq:USSMmu222Ot2Coeff}
